Second Year Paper Summary Statistics

### 2021-11-03 paper/report/summary_stats.Rmd
Adding main run.py script and consolidating/modularizing the maps code.

```{r packages, results='hide', message=FALSE, echo=F}
library(tidyverse)
library(foreign)
library(stargazer)
```
![Valid Purple Air Monitor Locations, Global](../../output/summary_stats/maps/purple_air_sensor_map_global.png)
![Valid Purple Air Monitor Locations, Contiguous United States](../../output/summary_stats/maps/purple_air_sensor_map_us.png)
![Valid Purple Air Monitor Locations, Global](../../output/summary_stats/maps/purple_air_sensor_map_california.png)

>>>>

```{r packages, results='hide', message=FALSE, echo=F}
library(tidyverse)
library(foreign)
library(stargazer)
```
![Valid Purple Air Monitor Locations, Global](../../output/summary_stats/maps/purple_air_sensor_map_world.png)
![Valid Purple Air Monitor Locations, Contiguous United States](../../output/summary_stats/maps/purple_air_sensor_map_us.png)
![Valid Purple Air Monitor Locations, Global](../../output/summary_stats/maps/purple_air_sensor_map_california.png)
